---
title: "R-Ladies Melbourne Inc 2019 highlights"
author: "Momeneh (Sepideh) Foroutan - 2019 President"
date: "January 2020"
output:
  html_document:
    theme: cosmo
    toc: yes
  word_document:
    toc: yes
  pdf_document:
    toc: yes
  github_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(magick)
library(png)
library(grid)
# devtools::install_github("hadley/emo")
# devtools::install_github("ropenscilabs/icon")
library(emo)
library(icon)

```

# R-Ladies chapters in Australia
As we mentioned [before](https://rladiesmelb2018.netlify.com), the R-Ladies Melb chapter was founded as the first R-Ladies chapter in Australia in Sep 2016. We are glad that today, there are five more chapters in Australia, including: \n

* [R-Ladies Sydney](https://www.meetup.com/en-AU/rladies-sydney/)
* [R-Ladies Brisbane](https://www.meetup.com/en-AU/rladies-brisbane/)
* [R-Ladies Canberra](https://www.meetup.com/en-AU/rladies-canberra/) 
* [R-Ladies Adelaide](https://www.meetup.com/en-AU/rladies-adelaide/) 
* [R-Ladies Perth](https://www.meetup.com/en-AU/rladies-perth/). 

Over the last three years, The R-Ladies Melb has had growing number of members, and today we are glad to have close to 1400 members in our [local community](https://www.meetup.com/en-AU/rladies-melbourne); this shows the existing need for an inclusive group for women and people of minority genders in the R community. 
The R-Ladies Melb had an amazing year in 2019; not only we registered the R-Ladies Melb as an incorporation, but also we received the Kellaway Excellence for Education Award from the Walter and Eliza Hall Institute of Medical Research (WEHI), hosted amazing speakers such as Alison and Hadley from RStudio and Melina from the editorial board of rOpensSci, and contributed in teaching to high school girls. Below are the highlights of R-Ladies Melb in 2019!

# R-Ladies Melb is now a registered not-for-profit!
As briefly mentioned [before](https://r-ladiesmelbourne-team.netlify.com), we started to learn about how to become an incoporated association over the last few months of 2018. Several members of the team started reading about this and collecting information, specifically [Anna Quaglieri](https://twitter.com/annaquagli), [Lucy Liu](https://twitter.com/lucyleeow) and [myself](https://twitter.com/S_Foroutan). Finally, in a lovely afternoon on the 29th of March, Lucy and I registered the **R-Ladies Melb Inc** through [myCAV for incorporated association](https://www.consumer.vic.gov.au/clubs-and-fundraising/incorporated-associations/mycav-for-incorporated-associations). This required us to define official roles, such as president, vice-president, treasurer and secretary. Then, we started learning how to open a bank account for incorporation and how to spend expenses and keep track of them more formally. A lot of these were done by [Adele Barugahare](https://twitter.com/technadele) who became our treasurer and [Marie Trussart](https://twitter.com/MTrussart), who was selected as vice-president in mid 2019 after our initial vice-president, [Nikki Rubinstein](https://twitter.com/nikkirubinstein), stepped down from that role due to other committment. [Goknur Giner](https://twitter.com/goknurginer) agreed to become the secretary after our intial secretary, Lucy, left Australia in May 2019; finally, I took the role of president.
```{r, echo=FALSE, fig.cap="Certificate of R-Ladies Melb Inc",echo=FALSE, fig.align="center", out.width = '80%'}
img <- readPNG("./photos/certificate_Inc.png")
grid.raster(img)
```

# Education award from WEHI
We are thrilled to be have been nominated for the **Kellaway Excellence Award for Education** by **Gordon Smyth** from WEHI, and very honored to have received this group award in Dec 2019. This is perhaps the first time that all the efforts of R-Ladies Melb have been officially recognised by an institute, and it feels incredibly great to have the support from the Bioinformatics co-division head and the director of WEHI, **Doug Hilton**. 
```{r, echo=FALSE, fig.cap="Receiving the Kellaway Excellence Award for Education from WEHI",echo=FALSE, fig.align="center", out.width = '90%', fig.asp=0.4}
img <- readPNG("./photos/award.png")
grid.raster(img)
```

# Alison and Hadley straight from the RStudio
This year, we were lucky to have two speakers from the RStudio: **Alison Hill** in Sep and **Hadley Wickham** in Nov 2019. [Alison Hill](https://twitter.com/apreshill?s=20) showed us how to take a bad plot and make it better! She gave an example of her work on a book and how she could make the same figure better and better every time! All of the attendees of that night also said a 'hi' to Alison's little daughter on the [video](https://twitter.com/apreshill/status/1179714814160957440?s=20) recorded by her! 
```{r, echo=FALSE, fig.cap="The R-Ladies Melb Inc event with Alison Hill",echo=FALSE, fig.align="center", out.width = '90%', fig.asp=0.4}
img <- readPNG("./photos/Alison.png")
grid.raster(img)
```
**[Di Cook](https://twitter.com/visnut?s=20)** has always supported the R-Ladies Melb team all along the way. In mid 2019, she informed us about [Hadley's](https://twitter.com/hadleywickham) visit to Melbourne later in the year. This allowed us to get in touch with Hadley and invite him straight away! Hadley's talk focused on designing data science. 
Perhaps it is not surprising that this event is the biggest event the R-Ladies Melb has organised to date. We had about 130 attendees and many people in the waiting list. That is why we live-streamed the event so that other people could join us too. We owe this to the amazing **Eike Germann** from [Eliiza](https://twitter.com/EliizaAI), who helped us with filming the event and streaming it live to our Youtube channel.
```{r, echo=FALSE, fig.cap="The R-Ladies Melb Inc event with Hadley Wickham",echo=FALSE, fig.align="center", out.width = '90%', fig.asp=0.8}
img <- readPNG("./photos/Hadley.png")
grid.raster(img)
```

Live streaming this event was extremely useful, and we had local and international people who could join us. Hadley not only covered materials related to the data science and importance of design, but also emphasized that people learn better through making mistakes and in a supportive environment. It was also fantastic to hear that he has given many talks at different R-Ladies groups in the world and that he believes the R-Ladies have made a supportive and friendly environment for people to learn. You can still watch [his talk on our Youtube](https://www.youtube.com/watch?v=bNVcDETgS54).
As we had so many people attending this event, we asked them to bring their own cup to minimise the waste. 
```{r, echo=FALSE, fig.cap="Tweets summarising the R-Ladies Melb Inc event with Hadley",echo=FALSE, fig.align="center", out.width = '90%', fig.asp = 0.3}
img <- readPNG("./photos/hadley_tweets.png")
grid.raster(img)
```

# Encouraging high school girls to code in R
We were invited to participate in the **“It takes a spark”** conference organized by Spark EDU in Sep 2019. This conference program is intended for both teachers and students to raise awareness and interest of high-school girls and connect with inspiring female role models. We organized a workshop on solving an outbreak using data analysis and programming skills. **Our goal was to empower high school girls and their teachers to learn how to code in R and solve a disease outbreak**. It was a great success as our workshop was booked out and it was a really rewarding experience that we thoroughly enjoyed. Special thanks to the enthusiasm of the students to learn and solve all the exercises. 
This workshop was prepared by Marie and Shazia, and was helped by Sehrish, Shanmathi and myself. We hope this workshop inspired many girls and contributed to overcome the bias in the low rate of female participation in science, technology, engineering, art and mathematics (STEAM) education and STEAM careers.

```{r, echo=FALSE, fig.cap=" It Takes a Spark conference for girls in STEAM",echo=FALSE, fig.align="center", out.width = '90%'}
img <- readPNG("./photos/ItTakesaSpark.png")
grid.raster(img)
```

# Co-founder of R-Ladies Melb and the R-Ladies Melb 3rd anniversary
The R-Ladies Melb Inc was excited to have Goknur Giner, co-founder of R-Ladies Melbourne, presenting about basics of RShiny during our third year anniversary event. Just to add a personal view on this, I started making my first RShiny app using my own data right after her super-clear talk on that day. We had an R-Ladies-themed cake with all the amazing members attended on the day and enjoyed a fantastic view from the NOUS venue. Morever, as I shared the great joy of founding this group with her, the moments Goknur talked about her journey with R-Ladies Melb were particularly sentimental to me. Her appreciation for the support she received from us as a community after she became a mother indicated that there are many other aspects of how R-Ladies Melb can assist individuals. Her daughter **Maya Su is 2.5 years old now and she has already been to two useR! conferences**. As Goknur mentioned in her talk, special thanks to the R-Ladies community all around the world for creating opportunities for women.   
```{r, echo=FALSE, fig.cap="The R-Ladies Melb third year annivesary with Goknur Giner",echo=FALSE, fig.align="center", out.width = '90%', fig.asp=0.45}
img <- readPNG("./photos/Goknur.png")
grid.raster(img)
```

# More advanced R
In 2019 we were able to organise 13 events covering workshops, seminars and networkings. Although we organised a workshop to teach the fundamentals of R (by **Goknur Giner** and **Nikki Rubinstein**) and a lunch Zoom event on the basic data visualisation in R (by **Zhuowen (Tobey) Zhang**), this year we focused more on the advanced topics; this was because the majority of our members were interested in advanced R topics, according to our 2019 start-of-the-year survey. Examples of these events were:\n

* RMarkdown and publication-ready documents by **Anna Quaglieri** and **Soroor Hediyeh Zadeh** in Feb
*	Overview of Reproducible research, documentation, and cloud computing by **Lavinia Gordon** in May
*	Natural language processing from **Ana Mamatelashvili** in Jun
*	Package review system and rOpenSci from **Melina Vidoni** in Jul
*	Reproducibility using Containers in R by **Saras Windecker** in Sep

```{r, echo=FALSE, fig.cap="Some of the R-Ladies Melb Inc events",echo=FALSE, fig.align="center", out.width = '90%'}
img <- readPNG("./photos/Rtalks.png")
grid.raster(img)
```


# Organisers of R-Ladies Melb Inc
The R-Ladies Melb has always had a main organiser for every year. Although we were not much formally shaped in 2017, **Goknur Giner** did a great job for organising sponsorships and venues, so she was our informal main organiser at the time. In 2018, **Anna Quaglieri** was selected more formally by all of us agreeing in our committee meeting for her to be the main organiser. Finally in Feb 2019, it was my turn to do it by everyone's agreement. The figure below shows the organisers of the R-Ladies Melb Inc in 2019 along with their roles. After calling for valounteers to be organisers of this group, [Shazia](https://twitter.com/DrShaziaRuybal?s=20), [Sehrish](https://twitter.com/skanwal23?s=20), Shanmathi and Miriam joined the team in Jun 2019. In addition to all of us, we also have had occasional help from **Stephanie Koo** for a couple of events; unfortunately, she did not have much time to commit as an official organiser.
```{r, echo=FALSE, fig.cap="R-Ladies Melb Inc Committee Members and Organisers",echo=FALSE, fig.align="center", out.width = '90%', fig.asp = 0.5}
img <- readPNG("./photos/RLadies_organisers.png")
grid.raster(img)
```

# Other contributions
In May 2019, Marie Trussart participated in an **Accelerated Leadership Program** (WLALPP MEL183) and made a [survey](https://docs.google.com/forms/d/e/1FAIpQLSeic80fjK4ZglkP5jN29YPExkjHCxSkTNgsg3JMNxInB8QfSg/viewform) to investigate the gender gap in STEM. It was great to have several male and female from the R-Ladies community filled out that survey.
Although useR! 2018 conference was in Brisbane and most of our organisers could attend and present at it, the **[useR! 2019](http://www.user2019.fr/)** in July 2019 was held in Toulouse, France and therefore harder for the organisers to attend that. However, it was fantastic to see that a past (Roxane) and a present (Goknur) R-Ladies Melb organisers could still meet up at the useR! 2019.
```{r, echo=FALSE, fig.cap="The useR! 2019 R-Ladies Global with Goknur and Roxane",echo=FALSE, fig.align="center", out.width = '90%', fig.asp=0.45}
img <- readPNG("./photos/RLadies_Group_France.png")
grid.raster(img)

```
**[Winter School in Mathematical and Computational Biology](http://bioinformatics.org.au/winterschool/speakers/)** is a yearly event organised by the University of Queensland and is designed to show university students and postdocs how to use bioinformatics and computational methods to solve biological questions. In Jul 2019, I was invited to talk about how to generate dynamic reports in RStudio and also introduce R-Ladies and its mission. It was my first time being on a speaker panel too!
For their event organised early in Dec 2019, we are happy that the **[Statsitical Society of Australia](https://twitter.com/StatSocAus)** (SSA) contacted the R-ladies Melb Inc to present and be a part of a panel discussion. Our amazing Anna Quaglieri agreed to give an overview of R-Ladies chapters with a focus on our group at their event. At the same time, many of the organising committee members were attending/presenting their work at the Australian Computational Biology and Bioinformatics Society (**[ABACBS](https://www.abacbs.org)**) and **[BioC Asia](https://bioconductor.github.io/BiocAsia/)**. 
```{r, echo=FALSE, fig.cap="Some of the other contributions of R-Ladies Melb members",echo=FALSE, fig.align="center", out.width = '90%', fig.asp = 0.8}
img <- readPNG("./photos/otherContributions.png")
grid.raster(img)
```

# STEM Women Changmakers grant
[Australian Academy of Science](https://twitter.com/Science_Academy?s=20) has made an [online directory](https://www.stemwomen.org.au) of Women who work in STEM in Australia, where women can share their profiles, and anyone can find them according to their experties and experiences. Late in 2019, **Lavinia Gordon** recommended that I should apply for the **STEM Women Changemakers grants** to attend the **["Catalysing Gender Equity"](https://aas.eventsair.com/catalysing-gender-equity/)** event in Adelaide; that was when I opened a women in STEM profile, and applied for the grants. I am very excied to have received one of the STEM Women Changemakers grants that are awarded to 12 women across Asutralia. I am grateful to Lavinia for letting me know about this and to the Australian Academy of Science for selecting me as one of the STEM Women Changmakers!
According to the record of Australian Academy of Science, there are > 2300 women who have joined STEM Women. I strongly encourage all women in STEM to open a profile and share all their contributions, so that their talent and expertise are accessible. 
```{r, echo=FALSE, fig.cap="Sepideh Foroutan wins an STEM Women Changemakers grant",echo=FALSE, fig.align="center", fig.asp = 0.35, out.width = '90%', fig.asp = 0.6}
img <- readPNG("./photos/WomenChangmakers.png")
grid.raster(img)
```


# How things work in terms of roles and rules
To be an organiser of R-Ladies Melb, you do not need to be expert in R, use R every day, and spend a lot of time organising things, etc; you can be an R-Ladies organiser if you are passionate about R, supportive of diversity in the R community, keen to help out with event organisation and have a bit of spare time. If you would like to get involved, here you can find a brief description of labor within the organising committee based on my experience. 

In addition to having **formal roles** defined by the incorporation (president, vice-president, secretary and treasurer), we also have our own **internal roles**.
For each role, we have a main person responsible for that role as well as a secondary person that covers that responsibility in the absence of the main person. Alternatively, the two people can share the responsibility as suit them. For example, Nikki and Shazia are responsible for the R-Ladies Melb twitter account, but for the events that Nikki was not around, Shaiza was the person doing the live-tweeting. They also check the R-Ladies Melb twitter account in turn. 

Not only we follow the **rules of incorporation**, but also we have always had our own **internal rules** which all members respect to. One of our internal rules, as we detailed before, is that there is **one/two main organiser(s) for each event**, who does not actually do all the things herself, but instead is responsible to follow up with different people responsible to do their tasks (venue booking, advertising, catering, etc). In this way, the responsibilities are split between all members across the year. We also defined new rules this year in terms of our **presence/absence** in the monthly organising committee meetings as well as in our monthly events. Based on this rule, if an organiser is absent in 3 consecutive meetings/events, she needs to be contacted by the president and checked if she is still inteersted to get involved.

If there are things that we are not sure about, we can always ask the other R-Ladies chapters on the slack channel, specifically, the **[R-Ladies Global](https://rladies.org)**. It is important to remember that all we do is voluntary and therefore there is no pressure to have so many events in a year; the more we can do, the more we enjoy supporting the under-represented people in the R community, which is a great cause and is truly rewarding.

If you think this is something that fits you and your schedule, please get in touch! The R-Ladies Melb always needs motivated and passionate organisers! 

# My personal remarks
I have been involved in the R-Ladies Melb chapter since the beginning, and for over three years now; two years as a co-organiser and last year as the president. During this time, I have learnt so much, not only about R and data analysis tools, but also about how to successfully organise events and how to share the work load as a team. I learnt so much about incorporations, found many new friends outside of academia, and expanded my network within academia.

It was a great but challenging experience to lead the team as the president. As a perfectionist, I always used to do everything myself, and so it was not easy to **delegate work to people**, but I am glad that I learnt this with help from other members, specifically, Marie and Goknur, whose encouragement and feedback gave me more confidence in my role as a leader. One thing that I used to do naturally though, was that I always **ask the committee members' opinions** on matters as it gave me a feeling that everyone is happy with a decision. 

**It has not been just about R!** This has been also about ourselves, our barriers and challenges. I believe the R-Ladies is a family where people offer support to each other! Sometimes this support is in the form of workshops or seminars, where people develop skills, which in turn may contribute to a [more inclusive data science world](https://qz.com/work/1661486/r-ladies-made-data-science-inclusive/), but other times, this support is in the form of friendship. I have experienced enormous amount of mental support from the members of R-Ladies Melb, particularly when I was hospitalised due to an accident early in 2019 and it was quite difficult to get back to my routine. I know other members in the team, such as Goknur as mentioned above, also benefited from the friendly and supportive environment in this family.

Based on all the great experience that I have had as a member of this community, **I strongly encourage you to consider joining the group as a co-organiser**. You can learn so much by doing so and see how rewarding it is! You will also be recognised for your contribution as we were, and of course it looks good on your CV! I am sure you will love being a part of this community, as we all do. 

In the end, I would like to thank every one of the past and the present **organisers** of R-Ladies, all our great **speakers** who shared their knowledge with our community in order to get them started using/making tools or advance their skills. It is obvious that without the **members in our local community** we would not be able to continue, and without the support that we get from the larger **community of R-Ladies** around the world we could not develop over time. It has been always the members' enthusiasm and the community's support that encouraged us to continue. THANK YOU!!

# Sponsors
Undoubtedly, without our faithful sponsors, we have not been able to be where we are today. A great thanks to all of them for their great support over years!
```{r, echo=FALSE, fig.cap="Our Amazing sponsors and the stunning view from the venue provided by NOUS",echo=FALSE, fig.align="center", out.width = '90%', fig.asp = 0.7}
img <- readPNG("./photos/Sponsors.png")
grid.raster(img)
```

# Testimonial
To be added later! I have asked Di and Lavinia to write something here.

# Find us 
Finally, do not forget to follow the R-Ladies Melb Inc if you would like to be updated about us and our events; we do our best to record our events, and make all of our events' materials available on Github.

* `r icon::fa("meetup",colour = "#88398A")` [Meetup](https://www.meetup.com/R-Ladies-Melbourne/)
* `r icon::fa("twitter",colour = "#88398A")` [Twitter](https://twitter.com/RLadiesMelb)
* `r icon::fa("facebook",colour = "#88398A")` [Facebook](https://www.facebook.com/RladiesMelbourne/)
* `r icon::fa("github",colour = "#88398A")` [Github](https://github.com/R-LadiesMelbourne)
* `r icon::fa("linkedin",colour = "#88398A")` [LinkedIN](https://www.linkedin.com/company/14675970/admin/)
* `r icon::fa("youtube",colour = "#88398A")` [YouTube](https://www.youtube.com/channel/UClC5yNEjMoE3MmbK-mrV8Ow/videos)

# Aknowledgements
I would like to thank Marie and Goknur for their valuable feedback about this document, as well as Anna for her great reports last year that I looked up to in order to produce this document.
